Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/compilation.tex
edits

Local preferences are now obtained by, for each router in the topology, sorting the corresponding PGIR nodes according to \textit{can prefer} relation. If two nodes are incomparable, then the compiler rejects the policy as unimplementable.

>>>>

For each router in the topology, local preferences are now obtained by  sorting the corresponding PGIR nodes according to the \textit{can prefer} relation. If two nodes are incomparable, the compiler rejects the policy as unimplementable.
